%==============================================================
% SEPARATE TITLE PAGE (NON-anonymous) for double-anonymous submission.
% Submit this separately from the anonymized main.tex.
% This is a standalone document; it compiles on its own with pdfLaTeX.
%==============================================================
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\begin{document}
\begin{center}
{\LARGE\bfseries Beyond Majority Vote: Improving Per-Requirement Quality\\[4pt]
Assessment via Good Outlier Recognition and Roundtable Consensus}
\end{center}

\bigskip
\noindent\textbf{Authors and Affiliations}

\begin{itemize}
  \item \textbf{[Author One]} — [Department], [Institution], [City], [Country]. ORCID: [0000-0000-0000-0000]
  \item \textbf{[Author Two]} — [Department], [Institution], [City], [Country].
  \item \textbf{[Author Three]} — [Department], [Institution], [City], [Country].
\end{itemize}

\noindent\textbf{Corresponding author:} [Author One], \href{mailto:corresponding@example.com}{corresponding@example.com}

\bigskip
\noindent\textbf{Acknowledgements.} [Optional. Add any acknowledgements here.]

\medskip
\noindent\textbf{Funding.} [State funding sources, or ``No funding was received for conducting this study.'']

\medskip
\noindent\textbf{Competing Interests.} The authors declare that they have no competing interests.

\medskip
\noindent\textbf{Author Contributions.} [Describe each author's contribution, e.g., conceptualization, methodology, experiments, writing.]

\medskip
\noindent\textbf{Data Availability.} The PURE dataset is publicly available; the replication package (requirement subsets, prompts, model outputs, ground-truth annotations, analysis scripts) will be released upon acceptance / available from the corresponding author on reasonable request.

\bigskip
\noindent\textit{Note.} The RE journal uses double-anonymous peer review and has migrated to the SNAPP system. Some declarations (competing interests, author contributions, funding) may need to be entered directly in the submission-system fields in addition to this title page. Please verify against the current journal instructions before submission.
\end{document}
